%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Yumeng He} \\ \vspace{1pt}
    \small 213-783-4223 $|$ \href{mailto:heyumeng@usc.edu}{\underline{heyumeng@usc.edu}} $|$ 
    \href{https://www.linkedin.com/in/yumeng-he}{\underline{linkedin.com/in/yumeng-he}} $|$
    \href{https://github.com/YumengHe}{\underline{github.com/YumengHe}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Southern California}{Los Angeles, CA, United States}
      {Master of Computer Science}{Aug 2024 -- Present}
      \resumeItemListStart
        \resumeItem{Expected to graduate at May 2026}
      \resumeItemListEnd
    \resumeSubheading
      {University of Toronto}{Toronto, ON, Canada}
      {Honours Bachelor of Science degree with High Distinction}{Sep 2019 -- May 2024}
      \resumeItemListStart
        \resumeItem{Computer Science and Mathematics double major}
        \resumeItem{Cumulative GPA: 3.71/4.0, highest Sessional Average: $92.40\%$.}
        \resumeItem{Dean’s Honors List for four years.}
        \resumeItem{Core courses: Computer Organization(A), Probability and Statistics II(A+), Interact Comp Media(A), Math Expr\&Rsng for Cs(A+), Design and Analysis of Data Structures }
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Developer Intern (1 year full-time)}{August 2022 – August 2023}
      {HCL Canada Inc.}{Toronto, ON, Canada}
      \resumeItemListStart
        \resumeItem{Acquired proficiency in Bash, Linux commands, Docker, Gradle, and Ant through a knowledge transfer training approach.}
        \resumeItem{Authored and regularly updated numerous scripts, including Jenkins files, to meet evolving project requirements.}
        \resumeItem{Designed an automation tool for efficient management of Jenkins logs, allowing customization of log retention and branch selection.}
        \resumeItem{Experimented with Jenkins pipeline configurations to enhance workflow processes.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
   % \resumeSubSubheading
   %  {Software Engineer I}{Oct 2014 - Sep 2016}
   %  \resumeItemListStart
   %     \resumeItem{Apache Beam}
   %       {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
   %  \resumeItemListEnd
   % \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Undergraduate Research Assistant}{May 2023 - August 2023}
      {Supervisor: Prof. Guangzhu Chen}{Remote}
      \resumeItemListStart
        \resumeItem{Proposed SS-Dualflow strategy to incorporate features from both normal and artificially generated abnormal samples into the Deep Learning Dual-Layer 2D Normalizing Flow network (Dualflow). }
        \resumeItem{Mapped features generated from the network to a Gaussian distribution, reducing information loss in the mapping process and bolstering the network’s capacity to comprehend common features in normal regions. }
        \resumeItem{Integration of the Exponential Space Attention Module into the inner subnetwork of Dualflow enabled the network to prioritize and distinguish anomalous features more effectively.}
        \resumeItem{The extended experimental outcomes on the MVTec AD dataset showcased an average image-level AUC of 99.38\% and an average pixel-level AUC of 98.38\%, demonstrating the approach's effectiveness.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Petpal } $|$ \emph{full-stack}}{Fall 2023}
          \resumeItemListStart
            \resumeItem{Headed a team of 4 in the development of a full-stack pet rescue website, enabling users to locate and report stray pets, access details about nearby rescue centers, and engage in group communication functions.}
            \resumeItem{Employed Django and Python for implementing the back-end service, while managing the database through MySQL.}
            \resumeItem{Contributed actively in weekly team meetings, documenting and monitoring teammates’ progress.}
            \resumeItem{Identified and resolved over 6 bugs, successfully clearing more than 20 unit test cases.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Interactive Computational Media Platform } $|$ \emph{full-stack	}}{Fall 2021}
          \resumeItemListStart
            \resumeItem{In a multidisciplinary design team of 6, collaborated to deliver an interactive and user-friendly website.}
            \resumeItem{Applied cutting-edge research methods in human-computer interaction.}
            \resumeItem{Participated in brainstorming, sketching, and designing prototypes aimed at solving real user problems; evaluated these prototypes for usability, learnability, and usefulness.}
            \resumeItem{High Fidelity Prototype: \href{https://unionoftrash.github.io/csc318f21-project-project4.0/index.html}{\underline{https://unionoftrash.github.io/csc318f21-project-project4.0/index.html}}}
          \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{Optimized System for Toronto Police Dispatch Response to Break and Enters} $|$ \emph{R}}{Spring 2020}
          \resumeItemListStart
            \resumeItem{Led and collaborated with a team of 6 in designing an optimized system using Artificial Intelligence for Toronto Police Force Distribution on Break and Enters through R.}
            \resumeItem{Visualized a dataset comprising 43,302 observations and 24 variables related to Break and Enter incidents.}
            \resumeItem{Concluded proportions of time zone occurrences by conducting one sample proportion hypothesis test, a bootstrap sample model, and two sample proportion hypothesis tests.}
            \resumeItem{Implemented a regression model to analyze the linear correlation among 6 years of occurrence data.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Proficient in utilizing technologies such as C/C++, Java, Python, R, RStudio, Dr. Racket, HTML, CSS, JavaScript, Docker, Gradle, Ant, and Shell command.} \\
     \textbf{Data Analysis}{: Well-acquainted with data analysis through Jupyter Notebook, encompassing various modules.} \\
     \textbf{Multilingual}{: Possesses excellent written and verbal communication abilities in both English and Mandarin.}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
