%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0pt}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabularx}{\textwidth}[t]{X r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabularx}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabularx}{\textwidth}{X r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabularx}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabularx}{\textwidth}[t]{X r}
        \textbf{#1} & #2 \\
    \end{tabularx}\vspace{-7pt}
}

% \newcommand{\resumeProjectHeading}[2]{
%     \item
%     \begin{tabularx}{\textwidth}[t]{X r}
%         \small\textbf{#1} & \small#2 \\
%     \end{tabularx}\vspace{-7pt}
% }


\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Yumeng He} \\ \vspace{1pt}
    \small 213-783-4223 $|$ \href{mailto:heyumeng@usc.edu}{\underline{heyumeng0928@gmail.com}} $|$ 
    \href{https://www.heyumeng.com} 
    {\underline{www.heyumeng.com}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Southern California}{Aug 2024 -- May 2026 (Expected)}
      {Master of Science in Computer Science}{Los Angeles, CA, USA}
      \resumeItemListStart
        \resumeItem{Relevant Courses: Computer Graphics}
      \resumeItemListEnd
    \resumeSubheading
      {University of Toronto}{Sep 2019 -- May 2024}
      {Honours Bachelor of Science degree with High Distinction}{Toronto, ON, Canada}
      \resumeItemListStart
        \resumeItem{Computer Science and Mathematics double major}
        \resumeItem{Dean's List Scholar for 4 semesters}
        \resumeItem{Cumulative GPA: 3.71/4.0, highest Sessional Average: $92.40\%$.}
        \resumeItem{Relevant Courses: Linear Algebra I, Linear Algebra II, Intro Machine Learning, Intro Artif Intell}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Working Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Software Developer Intern $|$ \normalfont full-time}{August 2022 – August 2023}
      {HCL Canada Inc.}{Toronto, ON, Canada}
      \resumeItemListStart
        \resumeItem{Utilized Jenkins to automate build and deployment processes and updated existing company code to address technical debt, significantly accelerating production releases and reducing human error.}
        \resumeItem{Built Docker images on both xLinux and pLinux platforms, ensuring consistent and scalable deployments.}
        \resumeItem{Integrated SonarQube into the development pipeline, documented a step-by-step usage guide, presented findings to cross-functional teams, and resolved 3 critical bugs plus 308 code smells (4 blockers, 41 major, 266 info).}
        \resumeItem{Developed a shell script to automatically clean up old logs every Sunday at 00:00 EST, preventing clutter and improving system performance.}
      \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Relevant Projects}
\resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{Ray Tracing} $|$ \normalfont C++}{Fall 2024}
        \resumeItemListStart
            \resumeItem{Developed a robust ray tracer in C++ capable of rendering both triangles and spheres using Phong shading, shadow rays, and recursive reflections for mirror-like surfaces.}
            \resumeItem{Implemented supersampling antialiasing, soft shadows from area lights, and the Möller–Trumbore algorithm for efficient ray–triangle intersections, enhancing visual realism and performance.}
        \resumeItemListEnd
        
    \resumeProjectHeading
        {\textbf{Simulating a Roller Coaster} $|$ \normalfont OpenGL}{Fall 2024}
        \resumeItemListStart
            \resumeItem{Implemented a first-person roller coaster simulator in C++ and OpenGL, harnessing Catmull-Rom splines for realistic track geometry and smooth camera orientation.}
            \resumeItem{Created multi-shader pipelines (texture mapping for ground, Phong shading for rails) with per-pixel lighting to achieve immersive, real-time visual effects.}
            \resumeItem{Added user-controlled speed, automated screenshot capture, and custom rail cross-sections for a fully interactive 3D experience.}
        \resumeItemListEnd

    \resumeProjectHeading
        {\textbf{Height Fields Using Shaders} $|$ \normalfont OpenGL}{Fall 2024}
        \resumeItemListStart
            \resumeItem{Built an interactive OpenGL pipeline with vertex and fragment shaders to generate real-time 3D terrain from heightmaps, supporting multiple rendering modes (points, lines, wireframe, smoothed surfaces).}
            \resumeItem{Integrated dynamic coloring, transformation/zoom controls, and automated screenshots/rotation features for an immersive, high-performance visualization experience.}
        \resumeItemListEnd
        
    % \resumeProjectHeading
    %     {\textbf{Petpal } $|$ \normalfont full-stack}{Fall 2023}
    %     \resumeItemListStart
    %         \resumeItem{Led a four-person team to develop a Python-based adoption platform using Django REST Framework, providing robust API endpoints for animal profiles, user authentication, and shelter–seeker communication.}
    %         \resumeItem{Created dynamic front-end interfaces with HTML, CSS, and JavaScript to ensure seamless and responsive user experiences across all devices.}
    %         \resumeItem{Employed MySQL for high-volume data storage and real-time updates, enabling secure and reliable handling of adoption records and user information.}
    %         \resumeItem{Integrated advanced search filters, personalized user profiles, and smooth navigation to optimize the pet adoption process for both seekers and shelters.}
    % \resumeItemListEnd
    \resumeProjectHeading
        {\textbf{Petpal} $|$ \normalfont Full-Stack}{Fall 2023}
        \resumeItemListStart
            \resumeItem{Led a four-person team to build a Python-based adoption platform with Django REST Framework, integrating MySQL for real-time data handling and advanced search filters.}
            \resumeItem{Implemented a responsive front end (HTML, CSS, JavaScript) and secure authentication to streamline the pet adoption process for seekers and shelters.}
    \resumeItemListEnd
    
\resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.0in, label={}]
    \small{\item{
     \textbf{Languages/Tools}{: Proficient in C++ and Python (with Jupyter), plus JavaScript (HTML/CSS), MySQL, Docker} \\
     \textbf{Graphics Experience}{: Developed real-time rendering pipelines (OpenGL, shaders) for interactive 3D projects} \\
     \textbf{Additional}{: Node.js, React, Gradle, Ant, R, Shell scripting} \\
     \textbf{Communication}{: Fluent in English and Mandarin}
    }
    }
 \end{itemize}


%-------------------------------------------
\end{document}
